Efficient Machine Learning in a Memristor Network

### 2025-02-10 paper/paper.tex
Starting branch to modify regression algorithm.

We broaden the training capability of the network by including a linear regression task, where, in its simplest form, the network is trained to give potential output $V^{\text{out}}$ related to the input potential $V^{\text{in}}$ via a linear relationship
\begin{equation}
    V_{\text{out}} = \text{c} V_{\text{in}} + \text{b}.
\label{eq:linear_relationship}
\end{equation}
Firstly, we generate a data set of input and output potential values, $\{ V^{in}_{i} \}_{i=1}^{}$ and $\{ V^{out}_{i} \}_{i}$ , that verify \cref{eq:linear_relationship}

>>>>

We broaden the training capability of the network by including a linear regression task, where, in its simplest form, the network is trained to give potential output $V^{\text{out}}$ related to the input potential $V^{\text{in}}$ via a linear relationship
\begin{equation}
    V_{\text{out}} = \text{c} V_{\text{in}} + \text{b}.
\label{eq:linear_relationship}
\end{equation}
Firstly, we generate a data set of $$ input and output potential values, $\{ V^{in}_{i} \}_{i=1}^{}$ and $\{ V^{out}_{i} \}_{i}$ , that verify \cref{eq:linear_relationship}
